Activity Recognition with mobile devices\\

### 2018-05-28 paper/main.tex
Related work

@@

\section*{List of Abbreviations}
\begin{acronym}[XXXXXXXX]
 \acro{AI}{Artificial Intelligence}
 \acro{GPS}{Global Positioning System}
 \acro{HAR}{Human Activity Recognition} 
\end{acronym}

>>>>

Concerning feature extraction different configurations chosen in the particular studies. Ravi et al. ~\cite{Ravi2005} for instance collected data for a window size of about 5.12 seconds using a sampling frequency of 50Hz while Kwapisz et al. ~\cite{Kwapisz2011} divided the data into segments of 10 seconds at sampling frequency of just 20Hz. Although the settings vary from each other the extracted features almost always are similar ~\cite{Ravi2005}. Typical features are
\begin{itemize}
\item mean
\item standard deviation
\item energy
\item correlation.
\end{itemize}

\begin{figure}[!htb]
\centering
\includegraphics[width=\linewidth]{different_activities}
\caption{A graph by Ravi et al. ~\cite{Ravi2005} showing the X-axis readings for different activities}
\label{fig:differentActivities}
\end{figure}
Like figure \ref{fig:differentActivities} is suggesting activities all have a certain pattern. Of course these patterns can be distinguished from each other as this is a basic requirement for detecting different activities. Therefore activities are mapped to classes, which requires classification techniques. A common toolkit for classification is the Weka toolkit that was called into action in many existing studies. Also different algorithms of this toolkit are compared as their performance as well as accuracy differs. Common algorithms are ~\cite{Ravi2005}
\begin{itemize}
\item decision tables
\item decision trees
\item k-nearest neighbors
\item \ac{SVM}
\item naive bayes.
\end{itemize}

@@

\section*{List of Abbreviations}
\begin{acronym}[XXXXXXXX]
 \acro{AI}{Artificial Intelligence}
 \acro{GPS}{Global Positioning System}
 \acro{HAR}{Human Activity Recognition}
 \acro{SVM}{Support Vector Machines}
\end{acronym}
